Systematic review of outbreak response models

### 2023-04-23 analyses/scripts/orv_sys_rev_data_analysis_old.Rmd
Set up global chunk settings

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Sets the working directory for subsequent chunks, but not this chunk
#knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

knitr::opts_chunk$set(fig.width = 8, fig.height = 6)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE, 
                      fig.width = 8, 
                      fig.height = 6
                      )
```
